---
title: "Comparisons with other data sets"
author: "ERM"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```
'

```{r loading packages, message=FALSE, warning=FALSE}

library(limma)
library(tidyverse)
library(ggsignif)
library(biomaRt)
library(RColorBrewer)
library(cowplot)
library(ggpubr)
library(scales)
library(sjmisc)
library(kableExtra)

```
# Knowles Comparison data:

```{r loading knowles data}
toplistall <- read.csv("output/toplistall.csv", row.names = 1)
backGL <- read.csv("data/backGL.txt",     row.names =1)
 drug_palNoVeh <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031")
drug_palc <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")
time <- rep((rep(c("3h", "24h"), c(6,6))), 6)
time <- ordered(time, levels =c("3h", "24h"))
drug <- rep(c("Daunorubicin","Doxorubicin","Epirubicin","Mitoxantrone","Trastuzumab", "Vehicle"),12)
indv <- as.factor(rep(c(1,2,3,4,5,6), c(12,12,12,12,12,12)))
labeltop <- (interaction(substring(drug, 0, 2), indv, time))
ensembl <- useMart("ensembl", dataset="hsapiens_gene_ensembl")
my_chr <- c(1:22, 'M', 'X', 'Y')  ## creates a filter for each
#attributes <- listAttributes((ensembl))
my_attributes <- c('entrezgene_id', 'ensembl_gene_id', 'hgnc_symbol')
level_order2 <- c('75','87','77','79','78','71')
# knowfig5<- Knowles_2018.elife.33480.supp5.v2 <- read.delim("~/Ward Lab/Cardiotoxicity/Manuscript/Knowles_2018-elife-33480-supp5-v2/Knowles_2018-elife-33480-supp5-v2")
# knowfig4 <- Knowles_2018.elife.33480.supp4.v2 <- read.delim("~/Ward Lab/Cardiotoxicity/Manuscript/Knowles_2018-elife-33480-supp4-v2/Knowles_2018-elife-33480-supp4-v2")
# write.csv(knowfig5,"data/knowfig5.csv")
# write.csv(knowfig4,"data/knowfig4.csv")

knowfig4 <- read.csv("data/knowfig4.csv",row.names = 1)
knowfig5 <- read.csv("data/knowfig5.csv",row.names = 1)

# covert ensg to entrezid -------------------------------------------------

knowles5 <- getBM(attributes=my_attributes,filters ='ensembl_gene_id',
                  values =knowfig5, mart = ensembl)
#377

knowles4 <- getBM(attributes=my_attributes,filters ='ensembl_gene_id',
                  values =knowfig4, mart = ensembl)
#524

knowles4 <-unique(knowles4$entrezgene_id)
knowles5 <-unique(knowles5$entrezgene_id)

all_QTLSknow<- union(knowles5,knowles4)

#total 794

```
  
Determining the genetic basis of anthracycline-cardiotoxicity by molecular
response QTL mapping in induced cardiomyocytes
David A Knowles, Courtney K Burrows†, John D Blischak,
Kristen M Patterson, Daniel J Serie, Nadine Norton, Carole Ober,
Jonathan K Pritchard, Yoav Gilad

Knowles $~~et~ al.~$ eLife 2018;7:e33480. DOI: https://doi.org/10.7554/eLife.33480
My first question was about transcription response at the 24 hour mark with my treatments.   3 hour RNA-seq had low levels of DEGs,so my focus is at 24 hours.  This also happens to be when the Knowles paper collected their RNA-seq data


Supplementary 4 contains a list of 518 SNPs within 1 Mb of TSS, which had a detectable marginal effect on expression (5% FDR). When converted from ensembl gene id to entrez gene id,  my list of unique Entrezgeneids = 521.  I will call these meSNPs for marginal effect snps.
In the meSNPs, 503 are within my DEG of 14084.  Using an adj. P value of 0.05, There are 199/6864 in 24 hour daunorubicin, 184/6516 in 24 hour doxorubicin, 182/6202 in 24 hour epirubicin, 30/1327 in 24 hour mitoxantrone and 0 in Trastuzumb

Supplementary 5 contains a list of 376 response eQTLs (reQTLs).  These are variants that were associated with modulation of transcriptomic response to doxorubicin treatment. After database name conversion, I have 377 unique Entregene ids.
Of the reQTLs list, 374 are within my DEG of 14084.  Using an adj. P value of 0.05, There are 187/6864 in 24 hour daunorubicin, 180/6516 in 24 hour doxorubicin, 176/6202 in 24 hour epirubicin, 40/1327 in 24 hour mitoxantrone and 0 in Trastuzumb.

  
```{r  knowles data comparisons}
dataframK_45 <- toplistall %>%
  mutate(id = as.factor(id)) %>%
  mutate(time=factor(time, levels=c("3_hours","24_hours"))) %>%
  filter(time== "24_hours") %>%
  group_by(time, id) %>%
  mutate(K4 = if_else(ENTREZID %in% knowles4,1,0))%>%
  mutate(K5 = if_else(ENTREZID %in% knowles5,1,0))%>%
  # filter(adj.P.Val<0.05) %>%
 summarize(n=n(), K4=sum(K4), K5=sum(K5)) %>% 
  as.data.frame()

sig05_dataframK_45 <- toplistall %>%
  mutate(id = as.factor(id)) %>%
  mutate(time=factor(time, levels=c("3_hours","24_hours"))) %>%
  filter(time== "24_hours") %>%
  group_by(time, id) %>%
  mutate(K4 = if_else(ENTREZID %in% knowles4,1,0))%>%
  mutate(K5 = if_else(ENTREZID %in% knowles5,1,0))%>%
   filter(adj.P.Val<0.05) %>%
 summarize(n=n(), K4=sum(K4), K5=sum(K5)) %>% 
  as.data.frame()
sig05_dataframK_45 %>% #mutate_at(.vars = 6, .funs= scientific_format()) %>% 
  kable(., caption= "Count of genes in each treatment by using adj. P value of <0.05") %>% 
  kable_paper("striped", full_width = FALSE) %>%  
  kable_styling(full_width = FALSE, position = "left",bootstrap_options = c("striped"),font_size = 18) %>% 
  scroll_box(width = "50%", height = "400px")
dataframK_45 %>% #mutate_at(.vars = 6, .funs= scientific_format()) %>% 
  kable(., caption= "Count of genes in each treatment by total expressed genes") %>% 
  kable_paper("striped", full_width = FALSE) %>%  
  kable_styling(full_width = FALSE, position = "right",bootstrap_options = c("striped"),font_size = 18) %>% 
  scroll_box(width = "50%", height = "400px")

```


```{r graphs of k4 k5 enrichment and FC}

 toplist24hr <-   toplistall %>%
  mutate(id = as.factor(id)) %>%
  mutate(time=factor(time, levels=c("3_hours","24_hours"))) %>%
  filter(time=="24_hours")
toplist24hr %>% 
  group_by(time, id) %>% 
  mutate(sigcount = if_else(adj.P.Val < 0.05,'sig','notsig'))%>%
  mutate(meSNP=if_else(ENTREZID %in%knowles4,"y","no")) %>% 
  mutate(reQTL=if_else(ENTREZID %in%knowles5,"a","b")) %>% 
  ggplot(., aes(x=id, y=abs(logFC)))+
  geom_boxplot(aes(fill=id))+
  fill_palette(palette =drug_palNoVeh)+
  guides(fill=guide_legend(title = "Treatment"))+
  facet_wrap(~time)+#,labeller = (time = facettimelabel) )+
  theme_bw()+
  xlab("")+
  ylab("abs |Log Fold Change|")+
  theme_bw()+
  facet_wrap(~time)+
  #ggtitle("All QTLs from all expressed genes (n=507)")+
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = 15, color = "black"),
        # axis.ticks = element_line(linewidth = 1.5),
        axis.line = element_line(linewidth = 1.5),
        strip.background = element_rect(fill = "transparent"),
        axis.text = element_text(size = 8, color = "black", angle = 0),
        strip.text.x = element_text(size = 12, color = "black", face = "bold"))+
  geom_signif(comparisons = list(c("Daunorubicin", "Doxorubicin"),
                                 c("Epirubicin", "Doxorubicin"),
                                 c("Mitoxantrone", "Doxorubicin"),
                                   c("Trastuzumab","Doxorubicin"),
                                 c("Mitoxantrone","Trastuzumab")),
                              test = "t.test",
              map_signif_level = FALSE,step_increase = 0.1,
              textsize = 4)
# This is a work in progress before vacation
# tabletoplist %>% ungroup() #%>% 
#   
#   select(time,id, sigcount, meSNP,n)
#   pivot_wider(id_cols = c(time,id), names_from=c(sigcount,meSNP), values_from=c(n)) #%>% 
#   mutate(propsig = sig/(sig+notsig)*100) %>% 
#   mutate(propsig=if_else(is.na(prop),0,prop))# %>% 
# mutate(propME = sig/(sig+notsig)*100) %>% 
#   mutate(propME=if_else(is.na(prop),0,prop))
# mutate(propRE = sig/(sig+notsig)*100) %>% 
#   mutate(propRE=if_else(is.na(prop),0,prop))
#   ggplot(., aes(x=id, y= prop))+
#   geom_col(aes(fill=id))+
#   geom_text(aes(label = sprintf("%.2f",prop)), position=position_dodge(0.9),vjust=-.2 )+
#   scale_fill_manual(values =drug_palNoVeh)+
#   guides(fill=guide_legend(title = "Treatment"))+
#   facet_wrap(id~time)+#labeller = (time = facettimelabel) )+
#   theme_bw()+
#   xlab("")+
#   ylab("Percentage of expressed genes")+
#   theme_bw()+
#   facet_wrap(~time)+
#   ggtitle("Percent DEGs (adj. P value <0.05)")+
#   theme(plot.title = element_text(size = rel(1.5), hjust = 0.5),
#         axis.title = element_text(size = 15, color = "black"),
#         # axis.ticks = element_line(linewidth = 1.5),
#         axis.line = element_line(linewidth = 1.5),
#         strip.background = element_rect(fill = "transparent"),
#         axis.text.x = element_text(size = 8, color = "white", angle = 0),
#         axis.text.y = element_text(size = 8, color = "black", angle = 0),
#         strip.text.x = element_text(size = 12, color = "black", face = "bold"))

   toplistall %>%
  mutate(id = as.factor(id)) %>%
  mutate(time=factor(time, levels=c("3_hours","24_hours"))) %>%
  mutate(sigcount = if_else(adj.P.Val < 0.05,'sig','notsig'))%>%
  mutate(meSNP=if_else(ENTREZID %in%knowles4,"y","no")) %>% 
  mutate(reQTL=if_else(ENTREZID %in%knowles5,"a","b")) %>% 
  filter(time =="24_hours") %>% 
  group_by(id,sigcount,meSNP) %>% 
  summarize(K4count=n()) %>% 
    pivot_wider(id_cols = c(id,sigcount), names_from=c(meSNP), values_from=K4count) %>% 
    mutate(K4prop=(y/(no+y))*100) %>% 
     ggplot(., aes(x=id, y=K4prop)) +
       geom_col()+
       geom_text(aes(x=id, label = sprintf("%.2f",K4prop), vjust=-.2))+
       #geom_text(aes(label = expression(paste0("number"~a,"out of",~b))))+
       facet_wrap(~sigcount)+
     ggtitle("non-significant and significant enrichment proporitions of Knowles min. eQTLS ")
  
  # KnowlesK5prop <- 
     toplistall %>%
  mutate(id = as.factor(id)) %>%
  mutate(time=factor(time, levels=c("3_hours","24_hours"))) %>%
  mutate(sigcount = if_else(adj.P.Val < 0.05,'sig','notsig'))%>%
  mutate(meSNP=if_else(ENTREZID %in%knowles4,"y","no")) %>% 
  mutate(reQTL=if_else(ENTREZID %in%knowles5,"a","b")) %>% 
  filter(time =="24_hours") %>% 
  group_by(id,sigcount,reQTL) %>% 
  summarize(K5count=n())%>% 
    pivot_wider(id_cols = c(id,sigcount), names_from=c(reQTL), values_from=K5count) %>% 
   mutate(K5prop=(a/(a+b)*100)) %>% 
       ggplot(., aes(x=id, y=K5prop)) +
       geom_col()+
       geom_text(aes(x=id, label = sprintf("%.2f",K5prop), vjust=-.2))+
       #geom_text(aes(label = expression(paste0("number"~a,"out of",~b))))+
       facet_wrap(~sigcount)+
       ggtitle("non-significant and significant enrichment proporitions of Knowles reQTLs ")
  
  

```




  
  
  
  
  
  
  

# Seaone 2019


Seone, Jose  Chromatin gene comparison:   comes from supp data NAT. MED 2019

```{r gene comparison, eval=TRUE, message=FALSE, warning=FALSE, include=FALSE}
library(readxl)

# Seoane_chromatinregs <- read_excel("C:/Users/renee/Downloads/Supplements folde manuscriptr/NIHMS1539805-supplement-SuppTables.xlsx", 
#     range = "A13:H469")

#write.csv(Seoane_chromatinregs, "data/Seonane2019supp1.txt")

chrom_reg_Seoane <- read_csv(file = "data/Seonane2019supp1.txt",col_types = cols(...1 = col_skip()))
                            
Seoane_2019 <- chrom_reg_Seoane[,2]
names(Seoane_2019) <- "ENTREZID"
chrom_genes <- (unique(Seoane_2019$ENTREZID))

toplist24hr %>% 
  mutate(id = as.factor(id)) %>%
  mutate(sigcount = if_else(adj.P.Val <0.05,'sig','notsig'))%>%
  mutate(chrom=if_else(ENTREZID %in%chrom_genes,"y","no")) %>% 
  group_by(id,sigcount,chrom) %>% 
  summarize(chromcount=n())%>% 
    pivot_wider(id_cols = c(id,sigcount), names_from=c(chrom), values_from=chromcount) %>% 
   mutate(chromprop=(y/(y+no)*100)) %>% 
       ggplot(., aes(x=id, y=chromprop)) +
       geom_col()+
       geom_text(aes(x=id, label = sprintf("%.2f",chromprop), vjust=-.2))+
       #geom_text(aes(label = expression(paste0("number"~a,"out of",~b))))+
       facet_wrap(~sigcount)+
       ggtitle("non-significant and significant enrichment proporitions of chromatin gene set ")

dataframchrom <- toplist24hr %>% 
  mutate(id = as.factor(id)) %>%
  mutate(sigcount = if_else(adj.P.Val <0.05,'sig','notsig'))%>%
  mutate(chrom=if_else(ENTREZID %in%chrom_genes,"y","no")) %>% 
  group_by(id,sigcount,chrom) %>% 
  summarize(chromcount=n()) %>% 
  as.data.frame()

dataframchrom %>%
  kable(., caption= "Significant (adj. P value of <0.05) and non-sig gene counts in Seoane geneset") %>% 
  kable_paper("striped", full_width = FALSE) %>%  
  kable_styling(full_width = FALSE, position = "left",bootstrap_options = c("striped"),font_size = 18) %>% 
  scroll_box(width = "60%", height = "400px")


##make table of numbers:


#genesof interest: 
# GWASsnps <- c('RARG', 'HIVEP1', 'ITGB7',  'PRDM2', 'KAZN', 'GDF5', 'FRS2', 'HDDC2', 'EEF1B2', 'SLC28A3')
# totalsnpgenes <- getBM(attributes=my_attributes,filters ='hgnc_symbol',
#                   values = GWASsnps, mart = ensembl)



```

# ArrGWAS to 24 hour DEG genes p < 0.05
```{r ArrGWAS}
# How I did the string split
# Arr_GWAS <- ArrGWAS[,13]
# names(Arr_GWAS) <- "genesplit"
# Arr_GWAS <- Arr_GWAS %>% 
#   separate_longer_delim(genesplit, delim = ",")
#write.csv(Arr_GWAS,"data/Arr_GWAS.txt")
toplist24hr <- toplistall %>%
  mutate(id = as.factor(id)) %>%
  mutate(time=factor(time, levels=c("3_hours","24_hours"))) %>%
  filter(time== "24_hours")
arr_GWAS <- read.csv("data/Arr_GWAS.txt", row.names = 1)
Arr_geneset <- getBM(attributes=my_attributes,filters ='hgnc_symbol',
                  values = arr_GWAS, mart = ensembl)
#remove duplicates
Arr_geneset <- Arr_geneset %>% distinct(entrezgene_id, .keep_all =TRUE)
#Apply sorting
toplist24hr %>% 
  mutate(id = as.factor(id)) %>%
  mutate(sigcount = if_else(adj.P.Val <0.05,'sig','notsig'))%>%
  mutate(ARR=if_else(ENTREZID %in%Arr_geneset$entrezgene_id,"y","no")) %>% 
  group_by(id,sigcount,ARR) %>% 
  summarize(ARRcount=n())%>% 
    pivot_wider(id_cols = c(id,sigcount), names_from=c(ARR), values_from=ARRcount) %>% 
   mutate(ARRprop=(y/(y+no)*100)) %>% 
       ggplot(., aes(x=id, y=ARRprop)) +
       geom_col()+
       geom_text(aes(x=id, label = sprintf("%.2f",ARRprop), vjust=-.2))+
       #geom_text(aes(label = expression(paste0("number"~a,"out of",~b))))+
       facet_wrap(~sigcount)+
       ggtitle("non-significant and significant enrichment proporitions of Arrhythmia GWAS ")

##make table of numbers:


dataframARR <- toplist24hr %>% 
  mutate(id = as.factor(id)) %>%
  mutate(sigcount = if_else(adj.P.Val <0.05,'sig','notsig'))%>%
  mutate(ARR=if_else(ENTREZID %in%Arr_geneset$entrezgene_id,"y","no")) %>% 
  group_by(id,sigcount,ARR) %>% 
  summarize(ARRcount=n()) %>% 
  as.data.frame()

dataframARR %>% #mutate_at(.vars = 6, .funs= scientific_format()) %>% 
  kable(., caption= "Significant (adj. P value of <0.05) and non-sig gene counts in Arrhythmia GWAS") %>% 
  kable_paper("striped", full_width = FALSE) %>%  
  kable_styling(full_width = FALSE, position = "left",bootstrap_options = c("striped"),font_size = 18) %>% 
  scroll_box(width = "60%", height = "400px")



```
# HFGWAS
```{r HFGWAS}
##just like ARrGWAS- imported the total csv, the took the "nearest" column and separated out the gene info
# test <- HFGWAS %>% 
#   select(nearest) %>% 
#   separate_wider_delim(nearest, delim = "[", names_sep = "", too_few = "align_start")
# test2 <- str_sub(test$nearest2,0,nchar(test$nearest2)-1)
# Hf_GWAS <- test2
#write.csv(Hf_GWAS, "data/Hf_GWAS.txt")
HF_GWAS <- read.csv("data/Hf_GWAS.txt", row.names =1)

HF_geneset <- getBM(attributes=my_attributes,filters ='hgnc_symbol',
                  values = HF_GWAS, mart = ensembl)
#remove duplicates
HF_geneset <- HF_geneset %>% distinct(entrezgene_id, .keep_all =TRUE)
#Apply sorting
toplist24hr %>% 
  mutate(id = as.factor(id)) %>%
  mutate(sigcount = if_else(adj.P.Val <0.05,'sig','notsig'))%>%
  mutate(HF=if_else(ENTREZID %in%HF_geneset$entrezgene_id,"y","no")) %>% 
  group_by(id,sigcount,HF) %>% 
  summarize(HFcount=n())%>% 
    pivot_wider(id_cols = c(id,sigcount), names_from=c(HF), values_from=HFcount) %>% 
   mutate(HFprop=(y/(y+no)*100)) %>% 
       ggplot(., aes(x=id, y=HFprop)) +
       geom_col()+
       geom_text(aes(x=id, label = sprintf("%.2f",HFprop), vjust=-.2))+
       #geom_text(aes(label = expression(paste0("number"~a,"out of",~b))))+
       facet_wrap(~sigcount)+
       ggtitle("non-significant and significant enrichment proporitions of Heart Failure GWAS ")

##make table of numbers:


dataframHF <- toplist24hr %>% 
  mutate(id = as.factor(id)) %>%
  mutate(sigcount = if_else(adj.P.Val <0.05,'sig','notsig'))%>%
  mutate(HF=if_else(ENTREZID %in%HF_geneset$entrezgene_id,"y","no")) %>% 
  group_by(id,sigcount,HF) %>% 
  summarize(HFcount=n()) %>% 
  as.data.frame()

dataframHF %>% #mutate_at(.vars = 6, .funs= scientific_format()) %>% 
  kable(., caption= "Significant (adj. P value of <0.05) and non-sig gene counts in HFhythmia GWAS") %>% 
  kable_paper("striped", full_width = FALSE) %>%  
  kable_styling(full_width = FALSE, position = "left",bootstrap_options = c("striped"),font_size = 18) %>% 
  scroll_box(width = "60%", height = "400px")








```

# CAD GWAS
```{r CADGWAS}
# test <- CADGWAS %>% 
#    select(nearest) %>% 
#    separate_wider_delim(nearest, delim = "[", names_sep = "", too_few = "align_start")
#  test2 <- str_sub(test$nearest2,0,nchar(test$nearest2)-1)
# 
# test2[c(32,38,44,74,112,126,191,212)] <- c("TPCN1","C2orf43","FAM222A", "TDRD15"  ,"AGPAT4","SVOP","SVOP","PLG")
#    
#  test2 [c(218,226,228,233,239,245,256,270,281,322,324,332,335,338,347,351,352,358)] <-  c("HPCAL1", "KLHL29"  , "COL4A3BP"  , "ARAP1" ,
#  "VEGFA", "TBPL1","SLC22A3" ,"C19orf38","LPA","VPS29","ATP2A2" ,"ATP2A2","KLHL29","GUCY1A3","KCNE2",  "HOXB9","P2RY2" ,"CTC-236F12.4")
#  
#  CAD_GWAS <- test2
#write.csv(CAD_GWAS, "data/cvd_GWAS.txt")
CAD_GWAS <- read.csv("data/cvd_GWAS.txt", row.names =1)

CAD_geneset <- getBM(attributes=my_attributes,filters ='hgnc_symbol',
                  values = CAD_GWAS, mart = ensembl)
#remove duplicates
CAD_geneset <- CAD_geneset %>% distinct(entrezgene_id, .keep_all =TRUE)
#Apply sorting
toplist24hr %>% 
  mutate(id = as.factor(id)) %>%
  mutate(sigcount = if_else(adj.P.Val <0.05,'sig','notsig'))%>%
  mutate(CAD=if_else(ENTREZID %in%CAD_geneset$entrezgene_id,"y","no")) %>% 
  group_by(id,sigcount,CAD) %>% 
  summarize(CADcount=n())%>% 
    pivot_wider(id_cols = c(id,sigcount), names_from=c(CAD), values_from=CADcount) %>% 
   mutate(CADprop=(y/(y+no)*100)) %>% 
       ggplot(., aes(x=id, y=CADprop)) +
       geom_col()+
       geom_text(aes(x=id, label = sprintf("%.2f",CADprop), vjust=-.2))+
       #geom_text(aes(label = expression(paste0("number"~a,"out of",~b))))+
       facet_wrap(~sigcount)+
       ggtitle("non-significant and significant enrichment proporitions of CAD GWAS ")

##make table of numbers:


dataframCAD <- toplist24hr %>% 
  mutate(id = as.factor(id)) %>%
  mutate(sigcount = if_else(adj.P.Val <0.05,'sig','notsig'))%>%
  mutate(CAD=if_else(ENTREZID %in%CAD_geneset$entrezgene_id,"y","no")) %>% 
  group_by(id,sigcount,CAD) %>% 
  summarize(CADcount=n()) %>% 
  as.data.frame()

dataframCAD %>% #mutate_at(.vars = 6, .funs= scientific_format()) %>% 
  kable(., caption= "Significant (adj. P value of <0.05) and non-sig gene counts in CAD GWAS") %>% 
  kable_paper("striped", full_width = FALSE) %>%  
  kable_styling(full_width = FALSE, position = "left",bootstrap_options = c("striped"),font_size = 18) %>% 
  scroll_box(width = "60%", height = "400px")

```


